### 2014-10-31 paper/include/refrint.tex
corrections

Four different policies can be applied for the cold rows, where the policies decide what to refresh; \textit{All}, \textit{Valid}, \textit{Dirty}, or \textit{WB(n,m)}. \textit{All} refreshes every row, regardless of whether it is valid or not. \textit{Valid} and \textit{Dirty} refreshes valid and dirty rows, respectively, and otherwise invalidate the row. \textit{WB(n,m)} refreshes a dirty row $n$ times before flushing it and changing the row state to valid clean, then the row is refreshed $m$ times after the last access before it is invalidated. Moreover, \textit{WB} is implemented using so called \textit{Count} bits, which is set either to $n$ or $m$ and is decremented upon refresh. % Mention the State bits as well?

@@

Refrint modifies the MC. The $N$ snapshot bits and a valid bit per DRAM row is stored in the MC and from experiments, Agrawal et al. found out that one or two are good values for $N$. To process the policies for the cold rows, decision logic as well as Count bits and State bits for each cache row is needed. Where the bits and logic resides is unclear to us, but they are placed outside the MC. In simulations, Agrawal et al. uses five Count bits, which give a negligible overhead and two bits for $N$. Of this, the total overhead became $0.005\%$, with a row size of \textit{8~KB}.

>>>>

Four different policies can be applied for the cold rows, where the policies decide what to refresh; \textit{All}, \textit{Valid}, \textit{Dirty}, or \textit{WB(n,m)}. \textit{All} refreshes every row, regardless of whether it is valid or not. \textit{Valid} and \textit{Dirty} refreshes valid and dirty rows, respectively, and otherwise invalidate the row. \textit{WB(n,m)} refreshes a dirty row $n$ times before flushing it and changing the row state to valid clean, then the row is refreshed $m$ times after the last access before it is invalidated. Moreover, \textit{WB} is implemented using so called \textit{Count} bits, which is set either to $n$ or $m$ and is decremented upon refresh, as well as a \textit{State} bit.

@@

Refrint modifies the MC. The $N$ snapshot bits and a valid bit per DRAM row is stored in the MC and from experiments, Agrawal et al. found out that one or two are good values for $N$. To process the policies for the cold rows, decision logic as well as Count bits and State bit for each cache row is is needed. The decision logic is placed outside the MC, loosely coupled with it, whereas the Count and State bits are stored in eDRAM logically with the data. In simulations, Agrawal et al. set Count to five bits and $N$ to two bits, resulting in a total overhead of $0.015\%$ if row size is \textit{8~KB}.
